
```{r}
#| warning: false

# calls script that has all the assigned objects for the text
source("NumberForInTextReport.r")

```

## Inquiries made to the Learning Collaborative

The total number of inquiries made since the Learning Collaborative (LC) launch is **`{r} tot_inq`** (see @fig-inquiries). Of these inquiries, `{r} LC_line` calls were made via the LC direct line, and `{r} Other_line` via other routes. Between the end of Q1 and now, the percentage change in inquiry numbers is **`{r} percentageChange`%**. 

```{r}
#| label: fig-inquiries
#| fig-cap: "Inquiries to STEP LC by region (a), and across time (b)"
#| fig-subcap: 
#|  - "Table of inquiries by region"
#|  - "Run chart of inquiries over time "
#| fig-align: center
#| warning: false
#| layout-ncol: 2

#calls the script that makes both the table and runchart
source("PSViz_Fig1a1b_inquiryRegionsTable&Runchart.r")
table1
inquiryRunchart
```

## Information about referrers - who made the inquiries?

```{r}
#| label: fig-referrersRoutes
#| fig-cap: "Referrals to the LC via clinical and community nodes. This is further split by how these groups heard about the initiative"
#| fig-subcap: 
#|  - "Community referral nodes"
#|  - "Clinical referral nodes"
#| fig-align: center
#| warning: false
#| layout-ncol: 2

#calls the script that makes both the clinical and community plots
source("PSViz_referrersClinical&Community_barchart.r")
referrersCommunityPlot
referrersClinicalPlot

# get summarys stats for text
commMax<-comm_df %>%
    summarise(n=n()) %>%
    filter(n==max(n)) 

clinMax<-clin_df %>%
    summarise(n=n()) %>%
    filter(n==max(n))  

```

Those referred to the LC via a clinical route primarily came via **`{r} clinMax$Clinical_Referral`**. Whereas for the community node, the **`{r} commMax$Community_Referral`** route has been the most prevelant. 

Referrers to the LC program heard about the initiative in various ways (see @fig-referrersRoutes). 

## Who was found to be eligible for the Learning Collaborative initiative?

So far, **`{r} Eligbile_Text$n`** people have been eligible for the LC, and **`{r} Under18_Text$n`** were aged under 18yrs (see @fig-EligXRegion). 

Individuals did not meet LC eligibility criteria for a range of reasons (n=**`{r} Ineligible_Text$n`**; see @fig-ineligibility) and were provided with appropriate information on referrals and resources.

Remaining cases are  either engaged in further assessment (n=`{r} PendingActivecases_text$n`), or remain unresolved (n=`{r} PendingInactivecases_text$n`).

```{r}
#| label: fig-EligXRegion
#| fig-cap: "Capturing eligibility information by region and age"
#| fig-subcap: 
#|  - "Eligibility rates by region"
#|  - "Pie chart showing age of eligible indivdiuals."
#| warning: false
#| layout-ncol: 2

#calls the script that makes the barchart eligible by region, and pie under 18
source("PSViz_eligibleXregion_bar&eligibleXage_Pie.r")
eligibleXregion_bar
eligibleUnder18_pie

```

```{r}
#| label: fig-ineligibility
#| fig-cap: "Barchart showing reasons for ineligibility to the LC"
#| warning: false

#calls the script for the barchat showing reasons for inelgibility
source("PSViz_IneligibleReasons_barchart.r")
gg3_bar

```

## Referrals to LMHAs across Connecticut


The **`{r} Eligbile_Text$n`** eligible individuals have been referred to their local mental health facilities. Of those, **`{r} number_admitted`** have been successfully admitted (see @tbl-tabLMHArefs_consent_new for  wait times by individual care facility). Below is a map of Connecticut. Here, we can see number of eligible cases by zipcode. 

```{r}
#| warning: false
#| fig-cap: "Heatmap of Connecticut, split by zipcodes, and coloured by number of indivdiuals currently found to be eligible for the LC"

#calls scripts that makes the eligibility map by zipcode
source("MAP_eligibeXzip.r")
p1_eligibleZips

```
```{r}
#| label: tbl-tabLMHArefs_consent_new
#| tbl-cap: "Table showing number average wait time to admission (date of consent to the LC to date of admission to care)."
#| warning: false

#calls the table with wait time from consenting to LC to admission to LMHA
source("PSViz_DUPTableLMHAs.r")
DUPTable

```

We had **`{r} number_not_admitted`** case where it can be determined that the individiual will not end up successfully enrolled at the 3 month mark (see @tbl-patients_rejected_referral_table). There are also **`{r} number_awaiting_admission`** cases where admission with the agency is yet to be confirmed. 

```{r}
#| label: tbl-patients_rejected_referral_table
#| tbl-cap: "Table showing number of eligible individuals where the referral did not land, and why"
#| warning: false

#calls script that makes the table showing reasons why patients didnt land
source("PSViz_tablePatientsNotAdmitted.r")
tablePatientsNotAdmitted
```
## Demographic and symptom data 

The following section provides an overview of individuals found to be eligible for the LC (n=**`{r} Eligbile_Text$n`**). Here, we provide information regarding the distribution of various baseline datapoints such as age, gender, race, income, and drug use.

```{r}
#| warning: false
#| label: fig-demos
#| fig-subcap: 
#|  - "Age group by gender (%)"
#|  - "Race category membership (%)"
#|  - "Bureau of labor statistic employment category; 1 square=1 person"
#|  - "Household and personal income (%)"
#| layout-ncol: 2

#calls script that make pyramid plot for age and gender
source("RCViz_demos_ageXgenderPyramidPlot.r")
pyramid_plot

#calls script that makes the barchart for race/ethnicity
source("RCViz_raceBar.r")
gg4

#calls script that makes the BLS employment waffle plot
source("RCViz_BLS_waffle.r")
gg1

#calls script that makes barchart for income
source("RCViz_incomebar.r")
incomeplot


```

```{r}
#| warning: false
#| label: fig-drugs
#| fig-cap: "Figure showing drug use as measured by the Alcohol Use and Drug Use scale"

#calls script that makes the drug/alcohol use barchart
source("RCViz_DRUGS_barchart.r")
gg2_drugsbar

```

```{r}
#| warning: false
#| label: fig-sympsAndsuicideet
#| fig-subcap: 
#|  - "Lifetime suicide and judicial involvement"

#calls script that makes lifetime suicide and judicial involvement plot
source("RCViz_suicideXlegalXviolence_bar.r")
gg2_bar

```
